### 2020-05-04 ncov.tex
am i done?

\section*{Abstract}
A novel coronavirus (SARS-CoV-2) has recently emerged as a global threat. 
As the epidemic progresses, disease modelers continue to focus on estimating the basic reproductive number \Ro\ --- the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro vary widely, despite relying on similar data sources.
Here, we present a novel statistical framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We then apply our framework to early estimates of \Ro for the SARS-CoV-2 outbreak.
We show that many early \Ro estimates are overly confident.
Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution, in efforts to estimate \Ro at the outset of an epidemic.

@@

Since December 2019, a novel coronavirus (SARS-CoV-2) has been spreading in many parts of the world \citep{pneumonia}.
Although the virus is likely to have originated from animal hosts \citep{andersen2020proximal}, the ability of SARS-CoV-2 to directly transmit between humans, particularly without symptoms, has posed a greater threat for its spread \citep{he2020temporal}.
As of March 2, 2020, more than 3 million cases of the coronavirus disease 2019 (COVID-19) have been confirmed internationally \citep{who103}.

@@

We present a statistical framework for averaging across estimates of basic reproductive number \Ro from multiple studies and apply the method to seven disparate models published online as pre-prints between January 23--26, 2020 that estimated \Ro for the SARS-CoV-2 outbreak \citep{bedfordncov, imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}.
Previous studies have directly calculated the average of reported \Ro values but such methods undermine differences in underlying model assumptions and statistical methods \citep{majumder2020early, liu2020reproductive}.
Instead, we decompose estimated \Ro into three key quantities ($r$, $\bar G$, and $\kappa$) and calculate the average (pooled estimates) of these key parameters.
Calculating \Ro based on the pooled estimates allow us to appropriately average across the uncertainties present in modeling approaches and their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval.
We also use our framework to tease apart which assumptions of these different models led to their different estimates and the associated degrees of uncertainty.

@@

\afterpage{%
\clearpage
    \begin{landscape}
\begin{table}[!th]
\begin{center}
\scriptsize
\begin{tabular}{l|p{2cm}|p{3.2cm}|p{2.8cm}|p{2.5cm}|p{2.4cm}|p{2.7cm}|p{2cm}}
 & Model & Data (study period) & Data source & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ & \\
\hline
Study 1 & Deterministic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 1.5--3.5 & 10 & 1 & \cite{bedfordncov} \\
\hline
Study 2 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0}  & 2.6 (1.5--3.5)$^\ast$ & 8.4 & Not reported$^\dagger$ & \cite{imaincov} \\
\hline
Study 3 & Poisson offspring distribution model & Confirmed cases from China and other countries\newline (Dec 29, 2019--Jan 23, 2020) & Medical records and epidemiological investigations from Guangdong Province, China, and official websites of other regions in China & 2.92 (95\% CI: 2.28--3.67) & 8.4 & 0.2 & \cite{liuncov} \\
\hline
Study 4 & Metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model & Confirmed cases from China\newline (Jan 1--21, 2020) & Not reported & 3.8 (95\% CI: 3.6--4.0) & 7.6 & 0.5 & \cite{readncov} \\
\hline
Study 5 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 2.2 (90\% CI: 1.4--3.8) & 7--14 & 0.5 & \cite{riouncov} \\
\hline
Study 6 & Exponential growth model & Confirmed cases from China\newline (Jan 10--22, 2020) & Wuhan
Municipal Health Commission, China and National Health Commission of China & 5.47 (95\% CI: 4.16--7.10)$^\ddagger$ & 7.6--8.4 & 0.2 & \cite{zhaoncov} \\
\hline
Study 7 & Incidence Decay and Exponential Adjustment (IDEA) model & Reported cases from Wuhan City, China\newline (Dec 1, 2019--Jan 26, 2020) & World	Health Organization, National Health Commission of China, Wuhan Municipal	Health Commission, and \cite{huang2020clinical} & 2.0--3.1 & 6--10 & 0 & \cite{majumderncov} \\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Summary of the models used and reported estimates of the basic reproductive number and the assumptions about the generation-interval distributions.}
Model details, estimates of \Ro, and their assumptions about the shape of the generation interval distributions were collected from 7 studies.
Generation-interval dispersion represent the squared coefficient of variations in generation intervals.
$^\ast$These intervals reflect \Ro values for best and worst scenarios. We treat these intervals as a 90\% credible interval in our analysis.
$^\dagger$We assume $\kappa = 0.5$ in our analysis.
$^\ddagger$The authors presented \Ro estimates under different assumptions regarding the reporting rate; we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
}
\end{table}
\end{landscape}
\clearpage
}

@@

When the epidemic is growing exponentially, the estimated basic reproductive number entirely depends on the exponential growth rate $r$ and the \emph{intrinsic} generation-interval distribution $g(\tau)$, which describes the infection time of secondary cases caused by a primary case in a fully susceptible population, via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
\frac{1}{\Ro} = \int \exp(-r\tau) g(\tau) \, d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, all model assumptions come down to assumptions about the exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.
For example, if a model relies on strong assumptions about the underlying observation or process model, the estimated confidence intervals associated with the exponential growth rates or parameters of the generation-interval distributions will be necessarily narrow.
Therefore, it is sufficient to consider the estimates and assumptions about the exponential growth rates and the shapes of the generation-interval distributions to understand disparate estimates of the basic reproductive number.

As most studies do not report their estimates of the exponential growth rate, we summarize model outcomes using reported (either estimated or assumed) values of the basic reproductive number \Ro, mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation (Table 1);
we re-estimate the corresponding exponential growth rates later.
Study 2 only reports their assumptions about the mean generation interval; for brevity, we assume $\kappa = 0.5$ in our analysis.
Study 6 presents \Ro estimates under 12 different scenarios regarding reporting rates (0, 0.5, 1 or 2 fold increase in reporting rate) and the shapes of the generation-interval distributions (MERS-like, SARS-like, and average);
we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
While estimates of \Ro and associated confidence intervals for Study 6 in Table 1 represents estimates of \Ro based on $\bar G = 8\,\mathrm{days}$, we account for the uncertainty they consider for $\bar G$ in our formal analysis.

@@

While some studies have now been published in peer-reviewed journals \citep{riou2020pattern, zhao2020preliminary} or have been updated with better uncertainty quantification \citep{readncov2}, we strictly focus on estimates that were published between January 23--26, 2020 for two reasons:
(i) to focus on the resolution of uncertainty in the earliest stages of an epidemic and
(ii) to illustrate that estimates of \Ro from different models can be understood by comparing their underlying assumptions about the exponential growth rates and generation-interval distributions.
We do not aim to provide more precise or accurate estimate of \Ro.

@@

As most studies do not report their estimates of the exponential growth rate, we first re-estimate the exponential growth rate that correspond to their model assumptions.
Since the estimates of the basic reproductive number \Ro entirely depends on the exponential growth rate and the shape of generation-interval distributions, we can calculate the exponential growth rate from the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
First, to account for uncertainties in these parameters, we model reported values of the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$ with appropriate probability distributions.
We used gamma distributions to model values reported with confidence/credible intervals and uniform distributions to model values reported with ranges;
when confidence/credible intervals are reported, we parameterize the gamma distribution such that (i) its mean matches the estimate value and (ii) the probability that a random variable following the specified gamma distribution falls between the lower and upper confidence/credible limits is equal to the reported confidence/credible level. This probability does not need to be equi-tailed.
For example, Study 3 estimated $\Ro = 2.92$ (95\% CI: 2.28--3.67);
we model this estimate as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).

For each study $i$, we construct a family of parameter sets by drawing $10^5$ random samples from the probability distributions (Table 2) that represent the estimates of $(\Ro)_{i,m}$ and the assumed values of $\bar G_{i,m}$ and $\kappa_{i,m}$ and calculate the exponential growth rate $r_{i,m}$ via the inverse of \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_{i,m} = \frac{\left[(\Ro)_{i,m}\right]^{\kappa_{i,m}} - 1}{\kappa_{i,m} \bar{G}_{i,m}},
\end{equation}
\end{linenomath*}
where $m=1,\dots,10^5$.
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study.
Uncertainties in the probability distributions that we calculate for the estimated exponential growth rates will reflect the methods and assumptions that the studies rely on.
Then, the set $(\bar{G}_{i}, \kappa_{i}, r_{i})$ defines an empirical parameter distribution for each study without having to re-fit each model.

For most cases, we model $(\Ro)_i$, $\bar G_i$, and $\kappa_i$ using independent distributions (as specified in Table 2) to calculate $r_i$.
In practice, this assumption does not affect our analysis because we are re-calculating the probability distribution of $r_i$ that is consistent with the reported values of $(\Ro)_i$, $\bar G_i$, and $\kappa_i$;
in other words, we still obtain the same estimates and the associated uncertainty of $(\Ro)_i$ if we calculate it from $r_i$, $\bar G_i$, and $\kappa_i$.
For study 6, we fix $\bar G=8\,\textrm{days}$ and use the gamma distribution (Table 2) that corresponds to $\mathcal R_0 = 5.47$ (95\% CI: 4.16--7.10) during the re-estimation step for $r$ to remain consistent with the original study that assumed $\bar G=8\,\textrm{days}$ to obtain this particular estimate;
the original article reports three $\mathcal R_0$ (and 95\% CIs) estimates using three different values of $\bar G$: 7.6 (MERS-like), 8 (average), and 8.4 (SARS-like) days.
We account for uncertainties in $\bar G$ for Study 6 (Table 1) in all other steps in order to properly incorporate parameter uncertainties in the estimate of \Ro.
Study 7 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling \Ro with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in the reported \Ro, when combined with the considered range of $\bar G$ in the original article.

\newcommand{\gammdist}{\mathrm{Gamma}}
\begin{table}[t]
\begin{center}
\scriptsize
\begin{tabular}{l|p{4.5cm}|p{2.5cm}|p{2.7cm}}
 & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ \\
\hline
Study 1 & $\mathrm{Uniform}(1.5, 3.5)$ & 10 & 1 \\
\hline
Study 2 & $\gammdist(\mathrm{mean}=2.6, \alpha=28)$ & 8.4 & 0.5 \\
\hline
Study 3 & $\gammdist(\mathrm{mean}=2.92, \alpha=67)$ & 8.4 & 0.2 \\
\hline
Study 4 & $\gammdist(\mathrm{mean}=3.8, \alpha=1400)$ & 7.6 & 0.5 \\
\hline
Study 5 & $\gammdist(\mathrm{mean}=2.2, \alpha=12)$ & $\mathrm{Uniform}(7, 14)$ & 0.5\\
\hline
Study 6 & $\gammdist(\mathrm{mean}=5.47, \alpha=54)$ & $\mathrm{Uniform}(7.6, 8.4)^\ast$ & 0.2\\
\hline
Study 7 & $\exp(r \bar G)^\dagger$ & $\mathrm{Uniform}(6, 10)$ & 0\\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for \Ro, $\bar G$, and $\kappa$.}
We use these probability distributions to obtain a probability distribution for the exponential growth rate $r$.
The gamma distribution is parameterized by its mean and shape $\alpha$.
Constant values are fixed according to Table 1.
$^\ast$We do not account for this uncertainty during our recalculation of the exponential growth rate $r$ because the reported estimate of $\mathcal R_0$ and its uncertainty assumes $\bar G = 8$; the original article reports three $\mathcal R_0$ (and 95\% CIs) estimates using three different values of $\bar G$: 7.6 (MERS-like), 8 (average), and 8.4 (SARS-like).
We still account for this uncertainty in our pooled estimates ($\mu_G$).
$^\dagger$Study 7 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling \Ro with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in the reported \Ro, when combined with the considered range of $\bar G$.
}
\end{table}

@@

We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters estimates across different studies come from the same gamma distributions:
\begin{linenomath*}
\begin{equation}
\begin{aligned}
(r_1, \dots, r_7) &\sim \gammdist(\mathrm{mean}=\mu_r, \mathrm{shape}=\mu_r^2/\sigma_r^2),\\
(\bar{G}_1, \dots, \bar{G}_7) &\sim \gammdist(\mathrm{mean}=\mu_G, \mathrm{shape}=\mu_G^2/\sigma_G^2),\\
(\kappa_1, \dots, \kappa_7) &\sim \gammdist(\mathrm{mean}=\mu_\kappa, \mathrm{shape}=\mu_\kappa^2/\sigma_\kappa^2),\\
\end{aligned}
\end{equation}
\end{linenomath*}
where $\mu_r$, $\mu_G$, $\mu_\kappa$ represent the pooled estimates, and $\sigma_r$, $\sigma_G$, and $\sigma_\kappa$ represent between-study standard deviations.
The pooled estimates, which are represented as probability distributions rather than point estimates, allow us to average across different modeling approaches, while accounting for the uncertainties in the assumptions they make.
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing a random set from the family of parameter sets for each study at each Metropolis-Hastings step.
Since the gamma distribution does not allow zeros, we use $\kappa=0.02$ instead for Study 7.

@@

We note that this approach does not account for non-independence between the parameter estimates made by different modelers.
In this case, most estimates primarily depend on by reported cases from China, particularly from Hubei province.
Differences among estimates are likely to reflect differences in estimation methods and underlying assumptions, rather than epidemiological differences.
The pooled estimates can become sharper (i.e., give narrower credible intervals) as we add more models even when the models no longer add more information about the epidemic.
Thus, the pooled estimator should be interpreted with care.

@@

We run 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps.
Posterior samples are thinned every 1000 steps to remove autocorrelation among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all hyperparameters \citep{gelman1992inference};
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by taking 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each parameter.

\subsection{Comparing estimates of the basic reproduction number}

In order to compare estimates of the basic reproduction number \Ro (and particularly their associated uncertainties) across different studies, we need a consistent measure of uncertainty.
Instead of using reported uncertainty ranges from the original studies, we re-calculate the basic reproduction number from the parameter sets ($r_i$, $\bar G_i$, and $\kappa_i$) for each study using \eref{gamma} and calculate the median and 95\% quantiles.
We refer to these estimates as the base estimates.
We note that the distribution of the basic reproduction number for each study corresponds to the assumed distributions in Table 2 for all studies except for Study 6.
The assumed distribution in Study 6 does not account for the uncertainty in the mean generation interval $\bar G$, whereas the base estimates account for this uncertainty.
Furthermore, since the distribution in Table 2 are constructed by matching the mean and the probabilities associated with the reported uncertainty ranges, the exact values of the base estimates and their 95\% quantiles could differ slightly from the reported values.
We compare the base estimates with pooled estimate the basic reproduction number \Rpool based on the pooled estimates of underlying parameters (by substituting $\mu_r$, $\mu_G$, $\mu_\kappa$ in \eref{gamma}).

>>>>

\section*{Abstract}
A novel coronavirus (SARS-CoV-2) has recently emerged as a global threat in December 2019. 
As the epidemic progresses, disease modelers continue to focus on estimating the basic reproductive number \Ro\ --- the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro during the beginning of the outbreak vary widely, despite relying on similar data sources.
Here, we present a novel statistical framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We then apply our framework to early estimates of \Ro for the SARS-CoV-2 outbreak.
We show that many early \Ro estimates are overly confident.
Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution, in efforts to estimate \Ro at the outset of an epidemic.

@@

Since December 2019, a novel coronavirus (SARS-CoV-2) has been spreading globally \citep{pneumonia}.
Although the virus is likely to have originated from animal hosts \citep{andersen2020proximal}, the ability of SARS-CoV-2 to directly transmit between humans, particularly without symptoms, has posed a greater threat for its spread \citep{he2020temporal}.
As of May 2, 2020, more than 3 million cases of the coronavirus disease 2019 (COVID-19) have been confirmed internationally \citep{who103}.

@@

We present a statistical framework for averaging across estimates of basic reproductive number \Ro from multiple studies and apply the method to seven disparate models published online as pre-prints between January 23--26, 2020 that estimated \Ro for the SARS-CoV-2 outbreak \citep{bedfordncov, imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}.
Previous studies have directly calculated the average of reported \Ro values  \citep{majumder2020early, liu2020reproductive} but such methods can undermine differences in underlying model assumptions and statistical methods.
Instead, we decompose estimated \Ro into three key quantities ($r$, $\bar G$, and $\kappa$) and calculate the average (pooled estimates) of these key parameters.
Calculating \Ro based on the pooled estimates allow us to appropriately average across the uncertainties present in modeling approaches and their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval.
% We also use our framework to tease apart which assumptions of these different models led to their different estimates and the associated degrees of uncertainty.

@@

\afterpage{%
\clearpage
    \begin{landscape}
\begin{table}[!th]
\begin{center}
\scriptsize
\begin{tabular}{l|p{2cm}|p{3.2cm}|p{2.8cm}|p{2.5cm}|p{2.4cm}|p{2.7cm}|p{2cm}}
 & Model & Data (study period) & Data source & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ & \\
\hline
Study 1 & Deterministic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 1.5--3.5 & 10 & 1 & \cite{bedfordncov} \\
\hline
Study 2 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0}  & 2.6 (1.5--3.5)$^\ast$ & 8.4 & Not reported$^\dagger$ & \cite{imaincov} \\
\hline
Study 3 & Poisson offspring distribution model & Confirmed cases from China and other countries\newline (Dec 29, 2019--Jan 23, 2020) & Medical records and epidemiological investigations from Guangdong Province, China, and official websites of other regions in China & 2.92 (95\% CI: 2.28--3.67) & 8.4 & 0.2 & \cite{liuncov} \\
\hline
Study 4 & Metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model & Confirmed cases from China and other countries\newline (Jan 1--21, 2020) & Not reported & 3.8 (95\% CI: 3.6--4.0) & 7.6 & 0.5 & \cite{readncov} \\
\hline
Study 5 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 2.2 (90\% CI: 1.4--3.8) & 7--14 & 0.5 & \cite{riouncov} \\
\hline
Study 6 & Exponential growth model & Confirmed cases from China\newline (Jan 10--22, 2020) & Wuhan
Municipal Health Commission, China and National Health Commission of China & 5.47 (95\% CI: 4.16--7.10)$^\ddagger$ & 7.6--8.4 & 0.2 & \cite{zhaoncov} \\
\hline
Study 7 & Incidence Decay and Exponential Adjustment (IDEA) model & Reported cases from Wuhan City, China\newline (Dec 1, 2019--Jan 26, 2020) & World	Health Organization, National Health Commission of China, Wuhan Municipal	Health Commission, and \cite{huang2020clinical} & 2.0--3.1 & 6--10 & 0 & \cite{majumderncov} \\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Summary of the models, analyzed data, reported estimates of the basic reproductive number, and the assumptions about the generation-interval distributions.}
Model details, estimates of \Ro, and their assumptions about the shape of the generation interval distributions were collected from 7 studies.
Generation-interval dispersion represent the squared coefficient of variations in generation intervals.
$^\ast$These intervals reflect \Ro values for best and worst scenarios. We treat these intervals as a 90\% credible interval in our analysis.
$^\dagger$We assume $\kappa = 0.5$ in our analysis.
$^\ddagger$The authors presented \Ro estimates under different assumptions regarding the reporting rate; we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
}
\end{table}
\end{landscape}
\clearpage
}

@@

When the epidemic is growing exponentially, the estimated basic reproductive number entirely depends on the exponential growth rate $r$ and the \emph{intrinsic} generation-interval distribution $g(\tau)$, which describes the infection time of secondary cases caused by a primary case in a fully susceptible population, via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
\frac{1}{\Ro} = \int \exp(-r\tau) g(\tau) \, d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, all model assumptions come down to assumptions about the exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.
For example, if a model relies on strong assumptions about the underlying observation or process model, the estimated confidence or credible intervals associated with the exponential growth rates or parameters of the generation-interval distributions will be necessarily narrow.
Therefore, it is sufficient to consider the estimates and assumptions about the exponential growth rates and the shapes of the generation-interval distributions to understand disparate estimates of the basic reproductive number.

As most studies do not report their estimates of the exponential growth rate, we first summarize model outcomes using reported (either estimated or assumed) values of the basic reproductive number \Ro, mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation (Table 1);
we re-estimate the corresponding exponential growth rates from these values later.
Study 2 only reports their assumptions about the mean generation interval; for brevity, we assume $\kappa = 0.5$ in our analysis.
Study 6 presents \Ro estimates under 12 different scenarios regarding reporting rates (0, 0.5, 1 or 2 fold increase in reporting rate) and the shapes of the generation-interval distributions (MERS-like, SARS-like, and average);
we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
While estimates of \Ro and the associated confidence intervals for Study 6 in Table 1 represents estimates of \Ro based on $\bar G = 8\,\mathrm{days}$, we account for the uncertainty they consider for $\bar G$ in our formal analysis.

@@

Some studies have now been published in peer-reviewed journals \citep{riou2020pattern, zhao2020preliminary} or have been updated with better uncertainty quantification \citep{readncov2}.
As our primary focus is on the resolution of uncertainty in the available information during the earliest stages of an epidemic, rather than to provide more precise or accurate estimate of \Ro, we strictly focus on estimates that were published between January 23--26, 2020.

@@

As most studies do not report their estimates of the exponential growth rate, we first re-estimate the exponential growth rate that correspond to their model assumptions.
Since the estimates of the basic reproductive number \Ro entirely depends on the exponential growth rate and the shape of generation-interval distributions, we can calculate the exponential growth rate from the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
First, to account for uncertainties in these parameters, we model reported values of the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$ with appropriate probability distributions.
We used gamma distributions to model values reported with confidence or credible intervals and uniform distributions to model values reported with ranges;
when confidence or credible intervals are reported, we parameterize the gamma distribution such that (i) its mean matches the estimated value and (ii) the probability that a random variable following the specified gamma distribution falls between the lower and upper confidence or credible limits is equal to the reported confidence or credible level. 
This probability does not need to be equi-tailed.
For example, Study 3 estimated $\Ro = 2.92$ (95\% CI: 2.28--3.67);
we model this estimate as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).

For each study $i$, we construct a family of parameter sets by drawing $10^5$ random samples from the corresponding probability distributions (Table 2) that represent the estimates of $(\Ro)_{i,m}$ and the assumed values of $\bar G_{i,m}$ and $\kappa_{i,m}$ and calculate the exponential growth rate $r_{i,m}$ via the inverse of \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_{i,m} = \frac{\left[(\Ro)_{i,m}\right]^{\kappa_{i,m}} - 1}{\kappa_{i,m} \bar{G}_{i,m}},
\end{equation}
\end{linenomath*}
where $m=1,\dots,10^5$.
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study.
We note that uncertainties in the probability distributions that we calculate for the estimated exponential growth rates reflects model assumptions, statistical methods, as well as quality of the data that each study relies on.
Then, the the family of parameter sets $(\bar{G}_{i,m}, \kappa_{i,m}, r_{i,m})$ defines an empirical parameter distribution for each study $i$ without having to re-fit each model.

For most cases, we model $(\Ro)_i$, $\bar G_i$, and $\kappa_i$ using independent distributions (as specified in Table 2) to calculate $r_i$.
This assumption does not affect our analysis because we are re-estimating the probability distribution of $r_i$ that is consistent with the reported values of $(\Ro)_i$, $\bar G_i$, and $\kappa_i$;
in other words, we still obtain the same estimates and the associated uncertainty of $(\Ro)_i$ if we calculate it from $r_i$, $\bar G_i$, and $\kappa_i$.
For study 6, we fix $\bar G=8\,\textrm{days}$ and use the gamma distribution (Table 2) that corresponds to $\mathcal R_0 = 5.47$ (95\% CI: 4.16--7.10) during the re-estimation step for $r$ to remain consistent with the original study that assumed $\bar G=8\,\textrm{days}$ to obtain this particular estimate.
We account for uncertainties in $\bar G$ for Study 6 (Table 1) in all other steps in order to properly incorporate parameter uncertainties in the estimate of \Ro.
Study 7 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling \Ro with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in the reported \Ro, when combined with the considered range of $\bar G$ in the original article.

\newcommand{\gammdist}{\mathrm{Gamma}}
\begin{table}[t]
\begin{center}
\scriptsize
\begin{tabular}{l|p{5cm}|p{2.5cm}|p{2.7cm}}
 & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ \\
\hline
Study 1 & $\mathrm{Uniform}(1.5, 3.5)$ & 10 & 1 \\
\hline
Study 2 & $\gammdist(\mathrm{mean}=2.6, \mathrm{shape}=18)$ & 8.4 & 0.5 \\
\hline
Study 3 & $\gammdist(\mathrm{mean}=2.92, \mathrm{shape}=67)$ & 8.4 & 0.2 \\
\hline
Study 4 & $\gammdist(\mathrm{mean}=3.8, \mathrm{shape}=1400)$ & 7.6 & 0.5 \\
\hline
Study 5 & $\gammdist(\mathrm{mean}=2.2, \mathrm{shape}=12)$ & $\mathrm{Uniform}(7, 14)$ & 0.5\\
\hline
Study 6 & $\gammdist(\mathrm{mean}=5.47, \mathrm{shape}=54)$ & $\mathrm{Uniform}(7.6, 8.4)^\ast$ & 0.2\\
\hline
Study 7 & $\exp(r \bar G)^\dagger$ & $\mathrm{Uniform}(6, 10)$ & 0\\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for \Ro, $\bar G$, and $\kappa$.}
We use these probability distributions to obtain a probability distribution for the exponential growth rate $r$.
The gamma distribution is parameterized by its mean and shape.
Constant values are fixed according to Table 1.
$^\ast$We do not account for this uncertainty during our re-estimation of the exponential growth rate $r$ because the reported estimate of $\mathcal R_0$ and its uncertainty assumes $\bar G = 8$.
We still account for this uncertainty in our pooled estimates ($\mu_G$).
$^\dagger$Instead of modeling \Ro with a probability distribution and re-estimating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in the reported \Ro, when combined with the considered range of $\bar G$.
}
\end{table}

@@

We construct pooled estimates for each parameter ($r$, $\bar G$, and $\kappa$) using a Bayesian multilevel modeling approach, which assumes that the parameters estimates across different studies come from the same gamma distributions:
\begin{linenomath*}
\begin{equation}
\begin{aligned}
(r_1, \dots, r_7) &\sim \gammdist(\mathrm{mean}=\mu_r, \mathrm{shape}=\mu_r^2/\sigma_r^2),\\
(\bar{G}_1, \dots, \bar{G}_7) &\sim \gammdist(\mathrm{mean}=\mu_G, \mathrm{shape}=\mu_G^2/\sigma_G^2),\\
(\kappa_1, \dots, \kappa_7) &\sim \gammdist(\mathrm{mean}=\mu_\kappa, \mathrm{shape}=\mu_\kappa^2/\sigma_\kappa^2),\\
\end{aligned}
\end{equation}
\end{linenomath*}
where $\mu_r$, $\mu_G$, $\mu_\kappa$ represent the pooled estimates, and $\sigma_r$, $\sigma_G$, and $\sigma_\kappa$ represent between-study standard deviations.
The pooled estimates, which are represented as probability distributions rather than point estimates, allow us to average across different modeling approaches, while accounting for the uncertainties in the assumptions they make.
We account for uncertainties associated with $r_i$, $\bar G_i$ and $\kappa_i$ (and their correlations), by drawing a random set from the family of parameter sets $(\bar{G}_{i,m}, \kappa_{i,m}, r_{i,m})$ for each study $i$ at each Metropolis-Hastings step.
Since the gamma distribution does not allow zeros, we use $\kappa=0.02$ instead for Study 7.

@@

We note that this approach does not account for non-independence between the parameter estimates made by different modelers.
In this case, most estimates primarily depend on reported cases from China, particularly from Hubei Province.
Differences among estimates are likely to driven by differences in estimation methods and underlying assumptions, rather than epidemiological differences.
The pooled estimates can become sharper (i.e., give narrower credible intervals) as we add more models even when the models or the data no longer add more information about the epidemic.
Since SARS-CoV-2 had primarily spread in Hubei Province, China during this period, it is not possible to include independent sources of data from other countries.
Thus, the pooled estimator should be interpreted with care.

@@

We run 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps.
Posterior samples are thinned every 1000 steps to remove autocorrelations among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all hyperparameters \citep{gelman1992inference};
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by taking 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each parameter.

\subsection{Comparing estimates of the basic reproductive number}

In order to compare estimates of the basic reproductive number \Ro (and particularly their associated uncertainties) across different studies, we need a consistent measure of uncertainty.
Instead of using reported uncertainty ranges from the original studies, we re-calculate the basic reproductive number from the parameter sets ($r_i$, $\bar G_i$, and $\kappa_i$) for each study using \eref{gamma} and calculate the median and 95\% quantiles.
We refer to these estimates as the base estimates.
We note that the distribution of the basic reproductive number for each study corresponds to the assumed distributions in Table 2 for all studies except for Study 6.
The assumed distribution in Study 6 in Table 2 does not account for the uncertainty in the mean generation interval $\bar G$, whereas the base estimates account for this uncertainty.
Furthermore, since the distribution in Table 2 are constructed by matching the mean and the probabilities associated with the reported uncertainty ranges, the exact values of the base estimates and their 95\% quantiles slightly differ from the reported values.
We compare the base estimates with pooled estimate the basic reproductive number \Rpool based on the pooled estimates of underlying parameters (by substituting $\mu_r$, $\mu_G$, $\mu_\kappa$ in \eref{gamma}).
